A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-14 ms.Rmd
Fixed one reference and added a reference on spatial scale of ecological traits

Clearly, many traits have been used to identify a species' adaptability with urban-living (e.g., Appendix 1), but often times results differ among studies. Fully understanding the suite of specific species' traits which are associated with urban birds allows for a better understanding of how to best preserve and maintain avian biodiversity in urban areas [@evans2011makes]. As previously noted, a major shortcoming of previous studies has been the focus on discrete classifications of species based on their responses to urbanization. Our analysis used a total of 477 species (Appendix 4), more than any similar study, to the best of our knowledge. Furthermore, our models assessed the applicability of traits in relation to one another (i.e., we did not run separate models or statistical tests for each specific trait as previously done). The aforementioned differences in our results compared with others is likely due to increased sample size, as well as our use of a continuous measure of urbanization. Our results suggest that urbanization selects against specialist species [@sorace2009distribution], granivores, and insectivores. As such, future urban development aimed at increasing avian diversity should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat]. A species-specific approach to assess particular resources necessary for specialist species may be necessary [@fernandez2004spatial]. Lastly, a focal point should be on increasing insect abundance and diversity in urban environments [@baldock2015uk], which will in turn increase the presence of insectivorous bird species in urban environments.

Global broad-scale empirical datasets are rapidly expanding our knowledge of urbanization impacts on birds [e.g., @aronson2014global, @aronson2016hierarchical, @gutierrez2018citizen], in large part due to the growing use of citizen science data [@silvertown2009new] in combination with advances in remote sensing technology [@gorelick2017google]. We used a novel approach, over a broad spatial and temporal scale, to quantify an urbanization index in birds. We did not explicitly account for changes throughout the annual cycle in a species' association with urban areas [e.g., @la2014role, @lepczyk2017global, @katewaleffect], but migratory status was considered as a predictor. We highlight that future studies, especially within migrant-dominated landscapes (e.g., Europe, North America), should account for changes in a species' response to urbanization throughout the full-annual cycle [@hostetler2015full, @marra2015call]. Further, future studies should look to expand this analysis outside the scope of Australia, and also investigate whether these patterns hold true at multiple spatial scales (i.e., does city size affect the patterns found here; [@sol2017urbanisation, @batary2018non]).

>>>>

Clearly, many traits have been used to identify a species' adaptability with urban-living (e.g., Appendix 1), but often times results differ among studies. Fully understanding the suite of specific species' traits which are associated with urban birds allows for a better understanding of how to best preserve and maintain avian biodiversity in urban areas [@evans2011makes]. As previously noted, a major shortcoming of previous studies has been the focus on discrete classifications of species based on their responses to urbanization. Our models assessed the applicability of traits in relation to one another (i.e., we did not run separate models or statistical tests for each specific trait as previously done). The aforementioned differences in our results compared with others is likely due to increased sample size, as well as our use of a continuous measure of urbanization. Our results suggest that urbanization selects against specialist species [@sorace2009distribution], granivores, and insectivores. As such, future urban development aimed at increasing avian diversity should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat]. A species-specific approach to assess particular resources necessary for specialist species may be necessary [@fernandez2004spatial]. Lastly, a focal point should be on increasing insect abundance and diversity in urban environments [@baldock2015uk], which will in turn increase the presence of insectivorous bird species in urban environments.

Global broad-scale empirical datasets are rapidly expanding our knowledge of urbanization impacts on birds [e.g., @aronson2014global, @aronson2016hierarchical, @gutierrez2018citizen], in large part due to the growing use of citizen science data [@silvertown2009new] in combination with advances in remote sensing technology [@gorelick2017google]. We used a novel approach, over a broad spatial and temporal scale, to quantify an urbanization index in birds. We did not explicitly account for changes throughout the annual cycle in a species' association with urban areas [e.g., @la2014role, @lepczyk2017global, @katuwaleffect], but migratory status was considered as a predictor. We highlight that future studies, especially within migrant-dominated landscapes (e.g., Europe, North America), should account for changes in a species' response to urbanization throughout the full-annual cycle [@hostetler2015full, @marra2015call]. Further, future studies should look to expand this analysis outside the scope of Australia, and also investigate whether these patterns hold true at multiple spatial scales [@suarez2018scale] (i.e., does city size affect the patterns found here; [@sol2017urbanisation, @batary2018non]).
